Meritocracy and distributive preferences ISSP

### 2020-08-06 production/prod_analysis.rmd
etiquetas
etiquetas a los graficos y arreglo de custom.note en tablas de reg

solo subo html y rmd de analisis

@@

@@

@@

```{r results='hide'}
plotredistgini<-plot_scatter(mer_pref_agg, gini_neto, redist, 
    title = "Desigualdad ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
	    	title = "Desigualdad (sin outliers)",
    	 fit.line = lm,
	    	show.ci = TRUE
		   	) + theme_classic()

plotredistfi<-plot_scatter(mer_pref_agg,  fi_index, redist, 
    title = "Libertad economica",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotredistfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, redist, 
    title = "Libertad economica (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

```{r results='hide'}
plotredistmerit <- plot_scatter(mer_pref_agg,  merit, redist, 
    title = "Percepcion meritocratica",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotredistbmerit <-plot_scatter(mer_pref_agg,  bmerit, redist, 
    title = "Preferencias meritocraticas",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotredistunmerit <-plot_scatter(mer_pref_agg,  unmerit, redist, 
    title = "Percepcion no meritocratica",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotredistneed <-plot_scatter(mer_pref_agg,  need, redist, 
    title = "Preferenciasno meritocraticas ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

```{r results='hide'}
plotaccumgini<-plot_scatter(mer_pref_agg, gini_neto, accum, 
    title = "Desigualdad ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotaccumgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, accum, 
	    	title = "Desigualdad (sin outliers)",
    	 #dot.labels = merit_agg$v5c,
	    	fit.line = lm,
	    	show.ci = TRUE
		   	)  + theme_classic()

@@

plotaccumfi<-plot_scatter(mer_pref_agg, fi_index, accum, 
    title = "Libertad economica",
    	#dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)   + theme_classic()

plotaccumfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, accum, 
    title = "Libertad economica (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)   + theme_classic()

@@

```{r results='hide'}
plotaccummerit <- plot_scatter(mer_pref_agg,  merit, accum, 
    title = "Percepcion meritocratica",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

plotaccumbmerit <-plot_scatter(mer_pref_agg,  bmerit, accum, 
    title = "Preferencias meritocraticas",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()
plotaccumunmerit <-plot_scatter(mer_pref_agg,  unmerit, accum, 
    title = "Percepcion no meritocratica",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()
plotaccumneed <-plot_scatter(mer_pref_agg,  need, accum, 
    title = "Preferenciasno meritocraticas ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotginimerit <- plot_scatter(mer_pref_agg,gini_neto,  merit,  
    title = "Percepcion meritocratica y desigualdad",
    #dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotginimerit_out <- plot_scatter(mer_pref_agg_zaf,gini_neto,  merit,  
    title = "Percepcion meritocratica y desigualdad (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotgfimerit <- plot_scatter(mer_pref_agg,fi_index,  merit,  
    title = "Percepcion meritocratica y libertad economica",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotgfimerit_out<- plot_scatter(mer_pref_agg_ven,fi_index,  merit,  
    title = "Percepcion meritocratica y libertad economica (sin outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotginibmerit <- plot_scatter(mer_pref_agg,gini_neto,  bmerit,  
    title = "Preferencias meritocraticas y desigualdad",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotginibmerit_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  bmerit,  
    title = "Preferencias meritocraticas y desigualdad (sin outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

plotfibmerit <- plot_scatter(mer_pref_agg,fi_index,  bmerit,  
    title = "Preferencias meritocraticas y libertad economica",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotfibmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  bmerit,  
    title = "Preferencias meritocraticas y libertad economica (sin outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotginiunmerit <- plot_scatter(mer_pref_agg,gini_neto,  unmerit,  
    title = "Percepcion no meritocratica y desigualdad",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotginiunmerit_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  unmerit,  
    title = "Percepcion no meritocratica y desigualdad (sin outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotfiunmerit <- plot_scatter(mer_pref_agg,fi_index,  unmerit,  
    title = "Percepcion no meritocratica y libertad economica",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotfiunmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  unmerit,  
    title = "Percepcion no meritocratica y libertad economica (sin outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotginineed <- plot_scatter(mer_pref_agg,gini_neto,  need,  
    title = "Preferencia no meritocratica y desigualdad",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()

@@

plotginineed_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  need,  
    title = "Preferencia no meritocratica y desigualdad (sin outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

plotfineed <- plot_scatter(mer_pref_agg,fi_index,  need,  
    title = "Preferencia no meritocratica y libertad economica",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

plotfineed_out <- plot_scatter(mer_pref_agg_ven,fi_index,  need,  
    title = "Preferencia no meritocratica y libertad economica (sin outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic()

@@

htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),caption = "Redistribution preference models", omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", custom.coef.names = c("Intercept", "Gini index", "Fi index", "Meritocratic perception", "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Interaction (GINI::Merit-perception)"), caption.above = T, star.symbol = "\\*", center = T, custom.note = "Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex")

@@

htmlreg(list(results_1_accum__1,results_1_accum__2, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), caption = "Accumulation preferences models", omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", custom.coef.names = c("Intercept", "Gini index", "Fi index", "Meritocratic perception", "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Interaction (Fi::Merit-perception)"), caption.above = T, star.symbol = "\\*", center = T, custom.note = "Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex")

@@

mer_accum_int_f2 <- sjPlot::plot_model(results_3_accum_macro_bvi_2, type = c("int"), title = "Interaccion Desigualdad") +  scale_color_discrete("Gini Index", labels = c("Min, Max"))

@@

results_1_redist_9 = lmer(redist ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref_sinnonconvr, REML=F)

results_1_redist_9_sinconvr = lmer(redist ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref, REML=F)

results_1_accum_9_sinnocon = lmer(accum ~ gini_neto + fi_index + merit + bmerit + unmerit + need + sstatus + as.factor(movstatus) + univ + as.factor(quintile_miss)  + sex + age  + 1 +  (1| v5c), data = mer_pref_sinnonconvr, REML=F)

@@

```{r results='asis'}
htmlreg(list(results_1_redist_9, results_1_redist_9_sinconvr, results_1_accum_9, results_1_accum_9_sinnocon), caption = "Comparison model excludig countries non convergent in the measurement", custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), caption.above = T, star.symbol = "\\*", custom.note = "countries non convergent in the measurement model:Venezuela, Croatia, Cyprus, Italy, Latvia") 
```

@@

htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_sininf,results_3_accum_macro_bvi, results_3_accum_macro_bvi_sininfl), caption = "Comparison model Without influential cases in level two", custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), caption.above = T, star.symbol = "\\*", custom.note = "Influential contries: CYP, TUR, TWN, UKR,CZE, FRA, AUS, DNK, USA, VEN,PHL, POL, CHN, ISR, CHL, LVA, PHL")

>>>>

![Correlation factor scores](../output/results/corplot_totscores.png)

@@

png("output/results/macrocor.png",width=600,height=600)

@@

![Macro level cor](../output/results/macrocor.png)

@@

```{r results='hide'}
plotredistgini<-plot_scatter(mer_pref_agg, gini_neto, redist, 
    title = "Redistribution and inequality",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()  + ylab("Redistribution preferences") + xlab("Gini index")

@@

plotredistgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, redist, 
	    	title = "Redistribution and inequality (without outliers)",
    	 fit.line = lm,
	    	show.ci = TRUE
		   	) + theme_classic() + ylab("Redistribution preferences") + xlab("Gini index")

plotredistfi<-plot_scatter(mer_pref_agg,  fi_index, redist, 
    title = "Redistribution and Economic freedom index",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Redistribution preferences") + xlab("Economic freedom index")

@@

plotredistfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, redist, 
    title = "Redistribution and Economic freedom index (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Redistribution preferences") + xlab("Economic freedom index")

@@

```{r results='hide'}
plotredistmerit <- plot_scatter(mer_pref_agg,  merit, redist, 
    title = "Redistribution and Meritocratic perception",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Redistribution preferences") + xlab("Meritocratic perception")

plotredistbmerit <-plot_scatter(mer_pref_agg,  bmerit, redist, 
    title = "Redistribution and Meritocratic preferences",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Redistribution preferences") + xlab("Meritocratic preferences")

plotredistunmerit <-plot_scatter(mer_pref_agg,  unmerit, redist, 
    title = "Redistribution and Unmeritocratic perception",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Redistribution preferences") + xlab("Unmeritocratic perception")

plotredistneed <-plot_scatter(mer_pref_agg,  need, redist, 
    title = "Preferenciasno meritocraticas ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Redistribution preferences") + xlab("Unmeritocratic preferences")

@@

```{r results='hide'}
plotaccumgini<-plot_scatter(mer_pref_agg, gini_neto, accum, 
      title = "Accumulation and Inequality ",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Accumulation preferences") + xlab("Gini index")

@@

plotaccumgini_outliers <- plot_scatter(mer_pref_agg_zaf, gini_neto, accum, 
	    	title = "Accumulation and Inequality (sin outliers)",
    	 #dot.labels = merit_agg$v5c,
	    	fit.line = lm,
	    	show.ci = TRUE
		   	)  + theme_classic() + ylab("Accumulation preferences") + xlab("Gini index")

@@

plotaccumfi<-plot_scatter(mer_pref_agg, fi_index, accum, 
    title = "Accumulation and Economic freedom",
    	#dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)   + theme_classic() + ylab("Accumulation preferences") + xlab("Ecconomic freedom index")

plotaccumfi_outliers<-plot_scatter(mer_pref_agg_ven,  fi_index, accum, 
    title = "Accumulation and Economic freedom (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)   + theme_classic() + ylab("Accumulation preferences") + xlab("Ecconomic freedom index")

@@

```{r results='hide'}
plotaccummerit <- plot_scatter(mer_pref_agg,  merit, accum, 
    title = "Accumulation and Meritocratic perception",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Accumulation preferences") + xlab("Meritocratic perception")

plotaccumbmerit <-plot_scatter(mer_pref_agg,  bmerit, accum, 
    title = "Accumulation and Meritocratic preferences",
    #	dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Accumulation preferences") + xlab("Meritocratic preferences")

plotaccumunmerit <-plot_scatter(mer_pref_agg,  unmerit, accum, 
    title = "Accumulation and Unmeritocratic perception",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Accumulation preferences") + xlab("Unmeritocratic perception")

plotaccumneed <-plot_scatter(mer_pref_agg,  need, accum, 
    title = "Accumulation and Unmeritocratic preferences",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Accumulation preferences") + xlab("Unmeritocratic preferences")

@@

plotginimerit <- plot_scatter(mer_pref_agg,gini_neto,  merit,  
    title = "Meritocratic perception and inequality",
    #dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Meritocratic perception") + xlab("Gini index")

@@

plotginimerit_out <- plot_scatter(mer_pref_agg_zaf,gini_neto,  merit,  
    title = "Meritocratic perception and inequality (sin outliers)",
    	#dot.labels = merit_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Meritocratic perception") + xlab("Gini index")

plotgfimerit <- plot_scatter(mer_pref_agg,fi_index,  merit,  
    title = "Meritocratic perception and Economic freedom",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Meritocratic perception") + xlab("Economic freedom index")

@@

plotgfimerit_out<- plot_scatter(mer_pref_agg_ven,fi_index,  merit,  
    title = "Meritocratic perception and Economic freedom (sin outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Meritocratic perception") + xlab("Economic freedom index")

@@

plotginibmerit <- plot_scatter(mer_pref_agg,gini_neto,  bmerit,  
    title = "Meritocratic preferences and inequality",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Meritocratic preferences") + xlab("Gini index")

@@

plotginibmerit_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  bmerit,  
    title = "Meritocratic preferences and inequality (without outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic()  + ylab("Meritocratic preferences") + xlab("Gini index")

plotfibmerit <- plot_scatter(mer_pref_agg,fi_index,  bmerit,  
    title = "Meritocratic preferences and Economic freedom",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Meritocratic preferences") + xlab("Economic freedom index")

@@

plotfibmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  bmerit,  
    title = "Meritocratic preferences and Economic freedom (without outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Meritocratic preferences") + xlab("Economic freedom index")

@@

plotginiunmerit <- plot_scatter(mer_pref_agg,gini_neto,  unmerit,  
      title = "Unmeritocratic perception and Inequality",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Unmeritocratic perception") +xlab("Gini index")

@@

plotginiunmerit_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  unmerit,  
    title = "Unmeritocratic perception and Inequality (without outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic perception") +xlab("Gini index")

plotfiunmerit <- plot_scatter(mer_pref_agg,fi_index,  unmerit,  
    title = "Unmeritocratic perception and Economic freedom",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic perception") + xlab("Economic freedom index")

@@

plotfiunmerit_out <- plot_scatter(mer_pref_agg_ven,fi_index,  unmerit,  
    title = "Unmeritocratic perception and Economic freedom (without outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic perception") + xlab("Economic freedom index")

@@

plotginineed <- plot_scatter(mer_pref_agg,gini_neto,  need,  
    title = "Unmeritocratic preferences and Inequality",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE) + theme_classic() + ylab("Unmeritocratic preferences") + xlab("Gini index")

@@

plotginineed_out<- plot_scatter(mer_pref_agg_zaf,gini_neto,  need,  
    title = "Unmeritocratic preferences and Inequality (without outliers)",
    #	dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic preferences") + xlab("Gini index")

plotfineed <- plot_scatter(mer_pref_agg,fi_index,  need,  
    title = "Unmeritocratic preferences and Economic freedom index ",
    #dot.labels = mer_pref_agg$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic preferences") + xlab("Economic freedom index")

@@

plotfineed_out <- plot_scatter(mer_pref_agg_ven,fi_index,  need,  
    title = "Unmeritocratic preferences and Economic freedom index (without outliers)",
    #	dot.labels = mer_pref_agg_ven$v5c,
    	fit.line = "lm",
    	show.ci = TRUE)  + theme_classic() + ylab("Unmeritocratic preferences") + xlab("Economic freedom index")

@@

htmlreg(list(results_1_redist__1, results_1_redist_3,results_1_redist_4,results_1_redist_5,results_1_redist_6,results_1_redist_7, results_1_redist_9, results_2_redist_macro_bv, results_3_redist_macro_bvi),caption = "Redistribution preference models", omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "GINI x Merit-perception"), caption.above = T, star.symbol = "\\*", center = T, custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex")

@@

htmlreg(list(results_1_accum__1,results_1_accum__2, results_1_accum_3,results_1_accum_4,results_1_accum_5,results_1_accum_6,results_1_accum_7, results_2_accum_macro_bv, results_3_accum_macro_bvi), caption = "Accumulation preferences models", omit.coef = "(sstatus)|(movstatus)|(univ)|(quintile_miss)|(age)|(sex)", custom.coef.names = c("Intercept", "Gini index", "Economic freedom index", "Meritocratic perception", "Meritocratic preference", "Unmeritocratic Perception","Unmerit preference", "Economic-freedom Merit-perception"), caption.above = T, star.symbol = "\\*", center = T, custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Since Model 6 control by subjetive status, mov subjetive status, Ed.univ, quintile_miss, age and sex")

@@

mer_accum_int_f2 <- sjPlot::plot_model(results_3_accum_macro_bvi_2, type = c("int"), title = "Interaccion Desigualdad") +  scale_color_discrete("Gini Index", labels = c("Min", "Max"))

@@

results_3_redist_macro_bvi_nocong = lmer(redist ~ univ + as.factor(quintile_miss) +    sstatus + as.factor(movstatus) + sex + age  + merit + bmerit + unmerit + need + merit*gini_neto + fi_index + 1 +  (1 + merit| v5c), data = mer_pref_sinnonconvr, REML=F)

results_3_accum_macro_bvi_nocong = lmer(accum ~ univ + as.factor(quintile_miss) +  sstatus + as.factor(movstatus) + sex + age  + merit + bmerit + unmerit + need +  gini_neto + merit*fi_index + 1 +  (1 + merit| v5c), data = mer_pref_sinnonconvr, REML=F)
```

```{r results='asis'}
htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_nocong, results_3_accum_macro_bvi, results_3_accum_macro_bvi_nocong), caption = "Comparison model excludig countries non convergent in the measurement", custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), star.symbol = "\\*", custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> countries non convergent in the measurement model:Venezuela, Croatia, Cyprus, Italy, Latvia", custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", "Subjetive upward mobility", "Supjetive downward mobility","Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", "Merit-perception x Gini", "Merit-perception x Economic-freedom"), caption.above = T)

@@

@@

htmlreg(list(results_3_redist_macro_bvi, results_3_redist_macro_bvi_sininf,results_3_accum_macro_bvi, results_3_accum_macro_bvi_sininfl), caption = "Comparison model Without influential cases in level two", custom.model.names = c("Whit", "Whithout","Whit", "Whithout"), custom.header = list("Redistribution" = 1:2, "Accumulation" = 3:4), caption.above = T, star.symbol = "\\*", custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05 <br> Influential contries: CYP, TUR, TWN, UKR,CZE, FRA, AUS, DNK, USA, VEN,PHL, POL, CHN, ISR, CHL, LVA, PHL", custom.coef.names = c("Intercept", "University. Ed.", "Quintile 2", "Quintile 3", "Quintile 4","Quintile 5", "Quintile miss", "Subjetive status", "Subjetive upward mobility", "Supjetive downward mobility" ,"Subjetive non-mobility","Gender", "Age", "Meritorcatic perception", "Meritocratic preferences", "Unmeritocratic perception", "Unmeritocratic preferences", "Gini index", "Economic freedom index", "Merit-perception x Gini", "Merit-perception x Economic-freedom"))
